---
documentclass: DissertateCUNY
title: 'Memory-guided selective attention: An instance theory of automatic attentional control'
author: Nicholaus P. Brosowsky
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: preamble.tex
    keep_tex: yes
mainfont: Times New Roman
bibliography: references.bib
csl: APA_format.csl
geometry: [top=1in, bottom=1in, right=1in, left=1in]
params:
  year: '2019'
  degree: 'Doctor of Philosophy'
  field: 'Psychology'
  chair: 'Matthew J.C. Crump, Ph.D.'
  advisor: 'Matthew J.C. Crump, Ph.D'
  committee1: 'Andrew R. Delamater, Ph.D.'
  committee2: 'Timothy J. Ricker, Ph.D.'
  committee3: 'Julie M. Bugg, Ph.D.'
  #committee4: '   '
  executiveOfficer: 'Richard Bodnar, Ph.D.'
  abstract: 'Cognitive control enables flexible goal-directed behavior via attention and action selection processes that prioritize goal-relevant over irrelevant information. These processes allow us to behave flexibly in the face of contradicting or ambiguous information and update behavior in response to the changing environment. Furthermore, they are thought to be in direct opposition to learned, automatic processing in that they enable us to disregard learned behaviors when they are inconsistent with our current goals. The strict dichotomy between stimulus-driven and goal-driven influences, however, has downplayed the role of memory in guiding attention. The position forwarded in this thesis is that a memory-based framework is needed to fully understand attentional control. People often re-encounter similar objects, tasks, and environments that require similar cognitive control operations. A memory-retrieval process could shortcut the slow, effortful, and resource-demanding task of updating control settings by retrieving and reinstating the control procedures used in the past. The aim of the current thesis is to empirically test general principles of an instance theory of automatic attentional control using a converging operations approach. In Chapter 2, I examine the obligatory nature of memory encoding by investigating context-specific proportion congruent effects in a non-conflict selective attention task. In Chapter 3, I examine the assumption of long-term instance-based representation by investigating long-term single-trial effects in a context-cuing flanker paradigm. Finally, in Chapter 4 I examine how memory retrieval can influence context-specific attentional control in a context-specific proportion congruent task.'

---

```{r global_options, include=FALSE}
# required packages
packages <- c("dplyr", "tidyr", "ggplot2", "afex", "papaja", "apaTables", "cowplot", "MBESS")
lapply(packages, require, character.only = T)

## This saves you from having to do this for every chunk
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

## Do NOT Remove / adds params to doc
cat(paste0("\\usepackage{xspace}\n",
      "\\newcommand{\\yeardegree}{",params$year,"\\xspace}",
      "\\newcommand{\\degree}{",params$degree,"\\xspace}\n",
      "\\newcommand{\\field}{",params$field,"\\xspace}\n",
      "\\newcommand{\\chairperson}{", params$chair, "\\xspace}\n",
      "\\newcommand{\\committeeone}{", params$committee1, "\\xspace}\n",
      "\\newcommand{\\committeetwo}{", params$committee2, "\\xspace}\n",
      "\\newcommand{\\committeethree}{", params$committee3, "\\xspace}\n",
      "\\newcommand{\\gradschoolguy}{", params$gradschool, "\\xspace}\n",
      "\\newcommand{\\EO}{", params$executiveOfficer, "\\xspace}\n",
      "\\newcommand{\\advisor}{", params$advisor, "\\xspace}\n",
      "\\newcommand{\\abstract}{", params$abstract, "\\xspace}\n",
      "% Tables
      \\usepackage{booktabs}
      \\usepackage{threeparttable}
      \\usepackage{array}
      \\newcolumntype{x}[1]{%
      >{\\centering\\arraybackslash}m{#1}}%
      \\usepackage{placeins}
      \\usepackage{chngcntr}
      \\counterwithin{figure}{chapter}
      \\counterwithin{table}{chapter}
      \\usepackage[makeroom]{cancel}\n"
      ),file = "preamble.tex")

```
<!-- Title page printed automatically -->
\copyrightpage
\approvalpage
\abstractpage 

<!-- Acknowledgements -->
\newpage
\fancyhead[L]{Acknowledgments}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{section}{Acknowledgments}

To my advisor, Dr. Matthew Crump, I am truly grateful for your constant guidance and exceptional mentorship. I am especially indebted to you for the many discussions we've had over the years. Because of you, this experience has been both rewarding and enjoyable. Thank you for always keeping me inspired, grounded, and focused on the big picture. It was a pleasure to learn from you, and the time we've spent together has meant a lot to me. I look forward to many more discussions to come.

To Dr. Randy Jamieson and Dr. Todd Mondor, thank you for your unwavering support over the years. You've both been in my corner rooting for me since the very beginning and I can't thank you enough for that. Your kind words and encouragement gave me the confidence to persevere and see this journey through to the end.

I would not be here without the support of my friends and family. To my parents, Ernie and Lil Brosowsky; my siblings, Jennie Rempel and Joey Brosowsky; and both of my extended families, the Careys and the Brosowskys, thank you for your love and continued support.

To my wife Taylor, thank you for being my partner in this adventure. With you by my side, I can accomplish anything. Thank you for being patient, supportive, and strong. You make this all worthwhile.

Finally, to my daughter Avery, thank you for coming along and giving me the swift kick in the butt I needed to get this thing finished!

<!-- Front Matter -->
\newpage
\fancyhead[L]{Table of Contents}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\tableofcontents

\newpage
\fancyhead[L]{List of Tables}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoftables

\newpage
\fancyhead[L]{List of Figures}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoffigures


\newpage
\pagenumbering{arabic}

<!-- Introduction -->
\newpage
\fancyhead[L]{GENERAL INTRODUCTION}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{GENERAL INTRODUCTION}
```{r child = 'chapters/ch-introduction.Rmd'}
```

\FloatBarrier

<!-- Chapter 2 -->
\newpage
\fancyhead[L]{INTENTIONAL CONTROL AS A PRE-REQUISITE FOR CONTEXTUAL CONTROL}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{INTENTIONAL CONTROL AS A PRE-REQUISITE FOR CONTEXTUAL CONTROL}

```{r child = 'chapters/ch-intentional-control.Rmd'}
```


\FloatBarrier

<!-- Chapter 3 -->
\newpage
\fancyhead[L]{SINGLE EXPERIENCES WITH CONFLICT}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{SINGLE EXPERIENCES WITH CONFLICT HAVE LONG-LASTING EFFECTS ON COGNITIVE CONTROL}

```{r child = 'chapters/ch-memory-guided.Rmd'}
```


\FloatBarrier
\newpage
\fancyhead[L]{CONTEXTUAL RECRUITMENT OF SELECTIVE ATTENTION}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{CONTEXTUAL RECRUITMENT OF SELECTIVE ATTENTION CAN BE UPDATED VIA CHANGES IN TASK-RELEVANCE}

```{r child = 'chapters/ch-task-relevance.Rmd'}

```

\FloatBarrier

<!-- Discussion -->
\newpage
\fancyhead[L]{GENERAL DISCUSSION}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{GENERAL DISCUSSION}

```{r child = 'chapters/ch-discussion.Rmd'}
```


\FloatBarrier

\newpage

\fancyhead[L]{REFERENCES}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{REFERENCES}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{6pt}
\noindent

<div id="refs"></div>
\clearpage